---
title: "p8015_hw5_xz2981"
author: "Xinyan Zhou"
date: "11/17/2021"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

Start with a dataframe containing all file names
```{r}
list_id <- list.files('./data')

list_df =
  tibble(
    id = list_id
  )
```

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
```{r}
add = function(x) {
  
  path <- paste0("./data/", x)
  
  data <-
    read_csv(file = path) %>%
    mutate(id = x)
  
  return(data)
  
}

data_temp =
  tibble(
    data = map(list_df,add)
  )
```

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
data_new <-
  data_temp %>%
  unnest(data) %>%
  select(id,everything()) %>%
  separate(id,c("arm","other"),sep = "_") %>%
  separate(other,c("id","other"),sep = "[.]") %>%
  select(-other) %>%
  pivot_longer( 
    week_1:week_8,
    names_to = "weeks", 
    names_prefix = "week_",
    values_to = "value")

data_new
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups
```{r}
data_new %>%
  ggplot(aes(x = weeks, y = value, group = id, color = arm)) +
  geom_line() +
  facet_grid(~arm) +
  labs(
    title = "Treatment value over time",
    x = "Week(s)",
    y = "Treatment value",
    caption = "Data from a longitudinal study"
  ) +
  theme_minimal()
```

In the control arm, we cannot find a clear pattern for the treatment value over time. The value for each individual seems to fluctuate randomly as the time changes.
In the experimental arm, we can find a clear pattern for the treatment value over time:
for each individual, the observed value increases as time goes by.

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()
```

Write a function that takes a vector as an argument

```{r}
fill_missing = function(x) {
  
  if (is.numeric(x)) {
    x = replace(x, which(is.na(x)), mean(x, na.rm = TRUE))
    }
  
  else {x = replace(x, which(is.na(x)), "virginica")}

  return(x)

}
```

Apply function  to the columns of iris_with_missing using a map statement

```{r}
output = map(iris_with_missing, fill_missing)

iris_no_missing = bind_rows(output)

iris_no_missing
```
